HMM Model development

### 2020-05-15 dev/hmm_model_devel.Rmd
Moving noisiness back to observed states

single_code <- make_stancode_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data, prior= data$observed_structured$prior)

@@

prepdata <- make_data_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data, sensitivity_low_bound = data$observed$sensitivity_low_bound)

standata <- make_standata_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data, sensitivity_low_bound = data$observed$sensitivity_low_bound)

>>>>

single_code <- make_stancode_hmm(data$observed_structured$formula, 
                                 serie_data = data$observed_structured$serie_data, 
                                 rate_data = data$observed_structured$rate_data, 
                                 hidden_state_data = data$observed_structured$hidden_state_data, 
                                 observed_state_data = data$observed_structured$observed_state_data,
                                 prior= data$observed_structured$prior)

@@

standata <- make_standata_hmm(data$observed_structured$formula, 
                              serie_data = data$observed_structured$serie_data, 
                              rate_data = data$observed_structured$rate_data, 
                              hidden_state_data = data$observed_structured$hidden_state_data, 
                              observed_state_data = data$observed_structured$observed_state_data,
                              sensitivity_low_bound = data$observed$sensitivity_low_bound)
